Poseidon Adventure

### 2021-09-30 CheckFisheryAnnageComp.Rmd
cod CAA from ANNAGECATCH diagnosis part I

---
title: "Generate data for NOBA cod SS3 modeling"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(atlantisom)
library(tidyverse)
library(ggthemes)

@@

@@

This dataset will come from NOBA sacc_30, with original biology, planned F + changes in selectivity for multiple groups, forced recruitment for groups	SCR+SSH+NCO, and climate change from	1981-2068+loop 2067..

>>>>

---
title: "Investigate fishery annual age comp issues"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
library(here)
library(atlantisom)
library(tidyverse)
library(ggthemes)

@@

There appears to be a problem with the fishery annual age output, especially for NOBA cod which has multiple fleets fishing it. Fishery annual age comps generated for "North_atl_cod" in Sept 2021 from NOBA sacc_38 and sacc_30 (without and with climate signal, but otherwise the same run) have the highest numbers for the oldest ages, which matches neither the aggregated fishery agecl age output nor the length comps generated from atlantisom. We'll try to figure out the problem and a fix here.

@@

This dataset will come from NOBA sacc_30, with original biology, planned F + changes in selectivity for multiple groups, forced recruitment for groups	SCR+SSH+NCO, and climate change from	1981-2068+loop 2067.

### What is in the ANNAGECATCH.nc file?

Load the `ANNAGECATCH.nc` file only for cod.
```{r}

fgs <- atlantisom::load_fgs(d.name, functional.groups.file)

bps <- atlantisom::load_bps(d.name, functional.groups.file, biomass.pools.file)

biol <- atlantisom::load_biolprm(d.name, biol.prm.file)

allboxes <- atlantisom::load_box(d.name, box.file)
boxes <- atlantisom::get_boundary(allboxes)

annagecatchnc <- atlantisom::load_nc_annage(dir = d.name, 
                                            file_nc = paste0(scenario.name, "ANNAGECATCH.nc"),
                                            file_fish = fisheries.file, 
                                            bps = bps,
                                            fgs = fgs,
                                            biolprm = biol,
                                            select_groups = "North_atl_cod",
                                            select_variable = "Catch",
                                            bboxes = boxes)

Visualize catch at age by fleet from full "true" output
```{r}

plotCAA <- function(dat){
  ggplot(dat, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  facet_wrap(~fleet) +
  labs(subtitle = dat$species)
}

At time = 1
```{r}
plotCAA(annagecatchnc %>%
          filter(time==1) %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```

At time = 200
```{r}
plotCAA(annagecatchnc %>%
          filter(time==200) %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```

At time = 320
```{r}
plotCAA(annagecatchnc %>%
          filter(time==320) %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```

At time = 490
```{r}
plotCAA(annagecatchnc %>%
          filter(time==490) %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```
Patterns here look identical over time, with a huge amount of catch of 17-20 year olds in the dtrawlNCO fishery.

Is this the same as what we would see in the omlist_ss output?

The true catch at annual age in this list is `NOBAom_ms$truecatchage_ss`, lets plot it
At time = 1
```{r}
plotCAA(NOBAom_ms$truecatchage_ss %>%
          filter(time==1,
                 species=="North_atl_cod") %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```
At time = 200
```{r}
plotCAA(NOBAom_ms$truecatchage_ss %>%
          filter(time==200,
                 species=="North_atl_cod") %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```

At time = 320
```{r}
plotCAA(NOBAom_ms$truecatchage_ss %>%
          filter(time==320,
                 species=="North_atl_cod") %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```

At time = 490
```{r}
plotCAA(NOBAom_ms$truecatchage_ss %>%
          filter(time==490,
                 species=="North_atl_cod") %>%
          group_by(species, agecl, fleet, time) %>%
          summarise(atoutput = sum(atoutput)))
```
Yes, these are identical.

Look at the file after create_fishery_subset

Look at the file after sample_fish

Compare with atlantisom output below

### 2021-09-30 docs/index.Rmd
add noba cod2 to index
cod CAA from ANNAGECATCH diagnosis part I

>>>>

### NOBA cod dataset take 2

Need to diagnose the annage outputs; they look strange

<a href="https://sgaichas.github.io/poseidon-dev/CheckFisheryAnnageComp.html" target="_blank"> Starting cod catch at annual age diagnosis, Sept 30, 2021</a>

<a href="https://sgaichas.github.io/poseidon-dev/NOBAcod2.html" target="_blank"> Multispecies dataset from NOBA sacc_30 with climate and fishery selectivity, Sept 29, 2021</a>
